\sysfull

### 2018-08-07 paper/asplos19/background.tex
revise background

\begin{figure}
    \begin{subfigure}{0.49\columnwidth}
        \includegraphics[width=\columnwidth]{figures/war-example.pdf}
        \caption{WAR-affected code}
        \label{fig:war-example}
    \end{subfigure}
    \begin{subfigure}{0.49\columnwidth}
        \includegraphics[width=\columnwidth]{figures/war-execution.pdf}
        \caption{WAR-affected code execution}
        \label{fig:war-execution}
    \end{subfigure}
    \caption{WAR dependency example. \texttt{NV} marks non-volatile variables, while \texttt{checkp()} is a checkpoint of volatile state.}
    \label{fig:war}
\end{figure}

@@

A power failure clears volatile state (e.g., registers and SRAM) while non-volatile memory (e.g., FRAM) persists. Upon a power failure, control flows to a prior point in the execution: by default, to the beginning of {\tt main()}. Early intermittent systems preserved progress by periodically checkpointing volatile execution context to non-volatile memory~\cite{mementos}, sometimes using hardware support~\cite{mottola2017harvos,hibernusplusplus,hibernus,idetic,quickrecall}. Checkpointing volatile state alone does not ensure data consistency when the system can directly manipulate non-volatile memory~\cite{mspcdino}. Precisely, data can get inconsistent when code includes a \emph{write-after-read} (WAR) dependency between operations that manipulate non-volatile memory. Fig.~\ref{fig:war} illustrates how state can become inconsistent in an intermittent execution using a simple example of an average operation over an array of integers.
The non-volatile variable \texttt{sum} introduces the WAR, being read and written sequentially by the increment operation. If a power failure occurs right before updating the non-volatile index \texttt{i} (\ref{fig:war-execution}, Line 6), \texttt{sum} gets erroneously incremented twice consecutively by the same array element (\ref{fig:war-execution}, Lines 5 and 8).

>>>>

\begin{figure}
    \begin{subfigure}{0.49\columnwidth}
        \includegraphics[width=\columnwidth]{figures/war-example.pdf}
        \caption{WAR-affected code}
        \label{fig:war-example}
    \end{subfigure}
    \begin{subfigure}{0.49\columnwidth}
        \includegraphics[width=\columnwidth]{figures/war-execution.pdf}
        \caption{WAR-affected code execution}
        \label{fig:war-execution}
    \end{subfigure}
    \caption{WAR dependency example. \texttt{NV} marks non-volatile variables, while \texttt{checkpoint()} is a checkpoint of volatile state.}
    \label{fig:war}
\end{figure}

@@

A power failure clears volatile state (e.g., registers and SRAM) while non-volatile memory (e.g., FRAM) persists. Upon a power failure, control flows to a prior point in the execution: by default, to the beginning of {\tt main()}. Early intermittent systems preserved progress by periodically checkpointing volatile execution context to non-volatile memory~\cite{mementos}, sometimes requiring hardware support~\cite{mottola2017harvos,hibernusplusplus,hibernus,idetic,quickrecall}, Table~\ref{table:chechpoint_comparison} summarizes the data that gets copied to and from the non-volatile memory in service of memory consistency and progress preservation. Checkpointing volatile state alone does not ensure data consistency when the system can directly manipulate non-volatile memory~\cite{mspcdino}. Precisely, data can get inconsistent when code includes a \emph{write-after-read} (WAR) dependency between operations that manipulate non-volatile memory. Fig.~\ref{fig:war} illustrates how state can become inconsistent in an intermittent execution using a simple example of an average operation over an array of integers.
The non-volatile variable \texttt{sum} introduces the WAR, being read and written sequentially by the increment operation. If a power failure occurs right before updating the non-volatile index \texttt{i} (\ref{fig:war-execution}, Line 6), \texttt{sum} gets erroneously incremented twice consecutively by the same array element (\ref{fig:war-execution}, Lines 5 and 8).
